%------------------------------------------------------------------------------------
% CouseTeX Simplified Latex Lightweight Open Course Web-framework
% [shane.transue@ucdenver.edu]
%------------------------------------------------------------------------------------
\documentclass[10pt]{article}
\input{courseinput.sty}

\begin{document}
\input{coursedoc.sty}

This is a module that may include information about OpenGL as an example.

\begin{section}{Graphical Processing Unit (GPU) Architecture}
This is some content that contains some math $\textstyle \vec{v} = \vec{a}\;\times\;\vec{b}$. Here is a bunch more text so that way it will fill in the remaining section of this page so hopefully there will be a second line eventually. This could be done using the lipsum package but I am lazy and this will have to do for now.

\begin{equation}
	\int_0^1 x^2 dx
\end{equation}

\lstinputlisting[caption=Scheduler Test]{code/test.c}

\begin{subsection}{Hello There Subsection}
	Hello subsection content. Here is some more content.
	
	\begin{equation}
		\int_0^1 x dx
	\end{equation}
\end{subsection}

\end{section}

\begin{section}{Some Random Section}
	Hello there some additional content of this section.
	
	\begin{subsection}{Subsection of Section 2}
		Here is some more content. Technically this could be done using lipsum.
	\end{subsection}
	
	\begin{subsection}{Another Subsection of Section 2}
		Here is some more content. Technically this could be done using lipsum, again.
	\end{subsection}
\end{section}

\begin{section}{Additional Section}
	Hello there some additional content of this section.
\end{section}
	
\end{document}
